\documentclass[letter,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{TLCresume} % Use the TLCresume.sty stylesheet for modern formatting

\begin{document}

\begin{flushleft}


%February 18, 2025\\[2em]

Hiring Team\\
Google DeepMind\\
Zurich, CH\\[2em]

Dear Hiring Team at Google DeepMind,\\[1em]

\onehalfspacing

\iffalse
My name is Matteo. Originally from Italy, I have lived in Basel for the past six years. I am excited to submit my application for the Machine Learning Software Engineer (Multilingual) position at Google DeepMind. 

My academic and professional journey is characterized by multidisciplinarity. With a background in Classics, I earned a PhD in Software Engineering with a focus on Machine Learning. My professional experience in digital data management within the humanities sector has provided invaluable opportunities to collaborate with diverse stakeholders across various domains, exposing me to different methodologies and fostering continuous growth.

Merging my humanities background with computer science was pivotal in creating the gold standard model that underpinned the classification system in my doctoral project. Without domain knowledge and an understanding of standard cataloging norms in the cultural heritage sector, I would not have been able to select and annotate art object descriptions for a comprehensive dataset. Domain and linguistic expertise are essential in tasks such as dataset creation and model fine-tuning.

This is precisely what motivated me to apply for this position: the opportunity to contribute with my hybrid background to the creation of impactful datasets and models at scale. I am confident that my experience can significantly contribute to defining datasets and fine-tuning models in Italian, Latin, and Ancient Greek, as well as models focused on cultural heritage.
\fi 

My name is Matteo. Originally from Italy, I have lived in Basel for the past six years. I am excited to submit my application for the Machine Learning Engineer position at Google DeepMind. 

My academic and professional journey is characterized by multidisciplinarity. With a background in Classics, I earned a PhD in Software Engineering with a focus on checking and evaluating the data and metadata quality in the cultural heritage domain using Machine Learning. My professional experience in digital data management within the humanities sector has provided invaluable opportunities to collaborate with diverse stakeholders across various domains, exposing me to different methodologies and fostering continuous growth.

Merging my humanities background with computer science was pivotal in improving the model that underpinned the classification system in my doctoral project. Without domain knowledge and an understanding of standard cataloging norms in the cultural heritage sector, I would not have been able to improve the accuracy of the classification model. This led to the large-scale integration of my model into the Italian digital library "Cultura Italia," impacting the quality control of metadata for approximately 5 million resources.

This is precisely what motivated me to apply for this position: the opportunity to contribute with my hybrid background to the improvement of impactful models at scale. I am confident that my experience can significantly contribute to improving the quality of language models with a focus on Italian, Latin, and Ancient Greek, as well as models focused on cultural heritage and history.

Thank you for your time and consideration.

Sincerely,\\[2em]

Matteo

\end{flushleft}

\end{document}