\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}


%====================
% EXPERIENCE A
%====================
\subsection{Research Scientist – Google Books Project \hfill April 2024 — Present}
\subtext{University Library Basel}
\begin{zitemize}
\item Leveraging LLM-driven NLP techniques to continuously classify and enhance Google Books metadata at scale for improved searchability and accuracy.
\item Designed and validated a balanced dataset of 60k multilingual (DE-FR-IT) resources, automatically annotated for a text classification task (topic classification).
\item Trained and fine-tuned a multilingual (DE-FR-IT) multilabel model for a text classification task (topic classification), achieving an F1 score of \textasciitilde 79\%.
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Ontologist II \hfill July 2022 --- April 2024}}
\subtext{Amazon}
\begin{zitemize}
\item Designed comprehensive, scalable ontologies and attributes to describe products, enhancing product discoverability, resulting in 11\% increase in Precision.
\item Designed a product compatibility reasoning pipeline leveraging LLMs, resulting in a 8\% reduction in inference time. 
\item Automated the attribute creation pipeline using LLMs and NLP techniques, generating 200+ high-quality attributes at scale and completing the Compatibility Program two months ahead of schedule.
\item Productionized and launched an LLM model for product classification, improving classification accuracy by 3\% across diverse product categories.

\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Research Scientist \hfill May 2019 --- June 2022}}
\subtext{ETH Zurich}
\begin{zitemize}
\item Designed a hybrid conceptual representation model of archival resources using RDF and OWL, advancing semantic interoperability.
\item Scaled the modeling of 150k archival records according to CIDOC-CRM ontology, enhancing data accuracy.
\item Optimized infrastructure scalability by automating manual processes and redesigning data pipelines for efficient delivery.

\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Research Scientist -Parthenos Project-\hfill May 2015 --- Apr. 2019}}
\subtext{Austrian Academy of Sciences}
\begin{zitemize}
%\item Supported humanities research by designing the PARTHENOS-PE ontology, enabling semantic interoperability.
\item Designed the CLARIN-CMDI metadata profile using CIDOC-CRM and PARTHENOS-PE ontology.
\item Scaled RDF graph creation with Python scripts, generating over 340k records.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Knowledge Graph Engineer\hfill May 2009 --- Dec. 2012}}
\subtext{Italian Ministry of Cultural Heritage}
\begin{zitemize}
\item Designed and modeled the PICO metadata schema in compliance with CIDOC-CRM ontology standards.
\item Designed Linked Open Data infrastructure for the Cultura Italia digital library.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}